Evaluating Class Imbalance

### 2019-07-23 Scripts/comparing_tad_regions_across_cl_using_vd.Rmd
updated with preprocessed tads

@@

binslist_gm12878_10kb <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/binslist10.rds")
binslist_gm12878_10kb_center <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/binslist10_center.rds")
mcols(binslist_gm12878_10kb)$y <- mcols(binslist_gm12878_10kb_center)$y
binslist_gm12878_10kb <- binslist_gm12878_10kb[mcols(binslist_gm12878_10kb)$y==1]

binslist_K562_10kb <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/binslist10.rds")
binslist_K562_10kb_center <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/binslist10_center.rds")
mcols(binslist_K562_10kb)$y <- mcols(binslist_K562_10kb_center)$y
binslist_K562_10kb <- binslist_K562_10kb[mcols(binslist_K562_10kb)$y==1]

res <- makeVennDiagram(Peaks=list(binslist_gm12878_10kb, binslist_K562_10kb),
                       NameOfPeaks=c("GM12878", "K562"))

venn_10kb <- venn_cnt2venn(res$vennCounts)
venn_10kb <- compute.Venn(venn_10kb)
gp <- VennThemes(venn_10kb)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "lightblue"
gp[["Face"]][["10"]]$fill <-  "red"
#plot(venn_10kb)

@@

binslist_gm12878_25kb <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/binslist25.rds")
binslist_gm12878_25kb_center <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/binslist25_center.rds")
mcols(binslist_gm12878_25kb)$y <- mcols(binslist_gm12878_25kb_center)$y
binslist_gm12878_25kb <- binslist_gm12878_25kb[mcols(binslist_gm12878_25kb)$y==1]

binslist_K562_25kb <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/binslist25.rds")
binslist_K562_25kb_center <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/binslist25_center.rds")
mcols(binslist_K562_25kb)$y <- mcols(binslist_K562_25kb_center)$y
binslist_K562_25kb <- binslist_K562_25kb[mcols(binslist_K562_25kb)$y==1]

res <- makeVennDiagram(Peaks=list(binslist_gm12878_25kb, binslist_K562_25kb),
                       NameOfPeaks=c("GM12878", "K562"))

venn_25kb <- venn_cnt2venn(res$vennCounts)
venn_25kb <- compute.Venn(venn_25kb)
gp <- VennThemes(venn_25kb)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "lightblue"
gp[["Face"]][["10"]]$fill <-  "red"
#plot(venn_25kb)

@@

binslist_gm12878_50kb <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/binslist50.rds")
binslist_gm12878_50kb_center <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/binslist50_center.rds")
mcols(binslist_gm12878_50kb)$y <- mcols(binslist_gm12878_50kb_center)$y
binslist_gm12878_50kb <- binslist_gm12878_50kb[mcols(binslist_gm12878_50kb)$y==1]

binslist_K562_50kb <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/binslist50.rds")
binslist_K562_50kb_center <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/binslist50_center.rds")
mcols(binslist_K562_50kb)$y <- mcols(binslist_K562_50kb_center)$y
binslist_K562_50kb <- binslist_K562_50kb[mcols(binslist_K562_50kb)$y==1]

res <- makeVennDiagram(Peaks=list(binslist_gm12878_50kb, binslist_K562_50kb),
                       NameOfPeaks=c("GM12878", "K562"))

venn_50kb <- venn_cnt2venn(res$vennCounts)
venn_50kb <- compute.Venn(venn_50kb)
gp <- VennThemes(venn_50kb)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "lightblue"
gp[["Face"]][["10"]]$fill <-  "red"
#plot(venn_50kb)

@@

binslist_gm12878_100kb <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/binslist100.rds")
binslist_gm12878_100kb_center <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/binslist100_center.rds")
mcols(binslist_gm12878_100kb)$y <- mcols(binslist_gm12878_100kb_center)$y
binslist_gm12878_100kb <- binslist_gm12878_100kb[mcols(binslist_gm12878_100kb)$y==1]

binslist_K562_100kb <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/binslist100.rds")
binslist_K562_100kb_center <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/binslist100_center.rds")
mcols(binslist_K562_100kb)$y <- mcols(binslist_K562_100kb_center)$y
binslist_K562_100kb <- binslist_K562_100kb[mcols(binslist_K562_100kb)$y==1]

res <- makeVennDiagram(Peaks=list(binslist_gm12878_100kb, binslist_K562_100kb),
                       NameOfPeaks=c("GM12878", "K562"))

venn_100kb <- venn_cnt2venn(res$vennCounts)
venn_100kb <- compute.Venn(venn_100kb)
gp <- VennThemes(venn_100kb)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "lightblue"
gp[["Face"]][["10"]]$fill <-  "red"
#plot(venn_100kb)

@@

gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_10kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("10 kb", gp=gpar(fontsize=20)))
grid.newpage()
gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_25kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("25 kb", gp=gpar(fontsize=20)))
grid.newpage()
gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_50kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("50 kb", gp=gpar(fontsize=20)))
grid.newpage()
gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_100kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("100 kb", gp=gpar(fontsize=20)))
grid.newpage()

>>>>

### 5kb

```{r}
#bounds_f_gm12878_5kb <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/training_testing/bounds_f.rds")
#bounds_f_K562_5kb <- readRDS("Z:/TAD_data_analysis/K562/5kb/training_testing/bounds_f.rds")

#res <- makeVennDiagram(Peaks=list(bounds_f_gm12878_5kb, bounds_f_K562_5kb),
#                       NameOfPeaks=c("GM12878", "K562"))

#venn_5kb <- venn_cnt2venn(res$vennCounts)
#plot(venn_5kb)

#binslist_gm12878_5kb <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/training_testing/binslist5.rds")
#binslist_gm12878_5kb_center <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/training_testing/binslist5_center.rds")
#mcols(binslist_gm12878_5kb)$y <- mcols(binslist_gm12878_5kb_center)$y
#binslist_gm12878_5kb <- binslist_gm12878_5kb[mcols(binslist_gm12878_5kb)$y==1]

#binslist_K562_5kb <- readRDS("Z:/TAD_data_analysis/K562/5kb/training_testing/binslist5.rds")
#binslist_K562_5kb_center <- readRDS("Z:/TAD_data_analysis/K562/5kb/training_testing/binslist5_center.rds")
#mcols(binslist_K562_5kb)$y <- mcols(binslist_K562_5kb_center)$y
#binslist_K562_5kb <- binslist_K562_5kb[mcols(binslist_K562_5kb)$y==1]

bounds_gm12878_5kb <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/training_testing/bounds_f.rds")
bounds_k562_5kb <- readRDS("Z:/TAD_data_analysis/K562/5kb/training_testing/bounds_f.rds")

res <- makeVennDiagram(Peaks=list(bounds_gm12878_5kb, bounds_k562_5kb),
                       NameOfPeaks=c("GM12878", "K562"))

venn_5kb <- venn_cnt2venn(res$vennCounts)
venn_5kb <- compute.Venn(venn_5kb)
gp <- VennThemes(venn_5kb)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "lightblue"
gp[["Face"]][["10"]]$fill <-  "red"
gp[["FaceText"]][["10"]]$cex <- 2
gp[["FaceText"]][["11"]]$cex <- 2
gp[["FaceText"]][["01"]]$cex <- 2
gp[["SetText"]][["Set1"]]$cex <- 2
gp[["SetText"]][["Set2"]]$cex <- 2

#plot(venn_5kb)

@@

#binslist_gm12878_10kb <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/binslist10.rds")
#binslist_gm12878_10kb_center <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/binslist10_center.rds")
#mcols(binslist_gm12878_10kb)$y <- mcols(binslist_gm12878_10kb_center)$y
#binslist_gm12878_10kb <- binslist_gm12878_10kb[mcols(binslist_gm12878_10kb)$y==1]

#binslist_K562_10kb <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/binslist10.rds")
#binslist_K562_10kb_center <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/binslist10_center.rds")
#mcols(binslist_K562_10kb)$y <- mcols(binslist_K562_10kb_center)$y
#binslist_K562_10kb <- binslist_K562_10kb[mcols(binslist_K562_10kb)$y==1]

bounds_gm12878_10kb <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/bounds_f.rds")
bounds_k562_10kb <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/bounds_f.rds")

res <- makeVennDiagram(Peaks=list(bounds_gm12878_10kb, bounds_k562_10kb),
                       NameOfPeaks=c("GM12878", "K562"))

venn_10kb <- venn_cnt2venn(res$vennCounts)
venn_10kb <- compute.Venn(venn_10kb)
gp <- VennThemes(venn_10kb)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "lightblue"
gp[["Face"]][["10"]]$fill <-  "red"
gp[["FaceText"]][["10"]]$cex <- 2
gp[["FaceText"]][["11"]]$cex <- 2
gp[["FaceText"]][["01"]]$cex <- 2
gp[["SetText"]][["Set1"]]$cex <- 2
gp[["SetText"]][["Set2"]]$cex <- 2
#plot(venn_10kb)

@@

#binslist_gm12878_25kb <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/binslist25.rds")
#binslist_gm12878_25kb_center <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/binslist25_center.rds")
#mcols(binslist_gm12878_25kb)$y <- mcols(binslist_gm12878_25kb_center)$y
#binslist_gm12878_25kb <- binslist_gm12878_25kb[mcols(binslist_gm12878_25kb)$y==1]

#binslist_K562_25kb <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/binslist25.rds")
#binslist_K562_25kb_center <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/binslist25_center.rds")
#mcols(binslist_K562_25kb)$y <- mcols(binslist_K562_25kb_center)$y
#binslist_K562_25kb <- binslist_K562_25kb[mcols(binslist_K562_25kb)$y==1]

bounds_gm12878_25kb <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/bounds_f.rds")
bounds_k562_25kb <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/bounds_f.rds")

res <- makeVennDiagram(Peaks=list(bounds_gm12878_25kb, bounds_k562_25kb),
                       NameOfPeaks=c("GM12878", "K562"))

venn_25kb <- venn_cnt2venn(res$vennCounts)
venn_25kb <- compute.Venn(venn_25kb)
gp <- VennThemes(venn_25kb)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "lightblue"
gp[["Face"]][["10"]]$fill <-  "red"
gp[["FaceText"]][["10"]]$cex <- 2
gp[["FaceText"]][["11"]]$cex <- 2
gp[["FaceText"]][["01"]]$cex <- 2
gp[["SetText"]][["Set1"]]$cex <- 2
gp[["SetText"]][["Set2"]]$cex <- 2
#plot(venn_25kb)

@@

#binslist_gm12878_50kb <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/binslist50.rds")
#binslist_gm12878_50kb_center <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/binslist50_center.rds")
#mcols(binslist_gm12878_50kb)$y <- mcols(binslist_gm12878_50kb_center)$y
#binslist_gm12878_50kb <- binslist_gm12878_50kb[mcols(binslist_gm12878_50kb)$y==1]

#binslist_K562_50kb <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/binslist50.rds")
#binslist_K562_50kb_center <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/binslist50_center.rds")
#mcols(binslist_K562_50kb)$y <- mcols(binslist_K562_50kb_center)$y
#binslist_K562_50kb <- binslist_K562_50kb[mcols(binslist_K562_50kb)$y==1]

bounds_gm12878_50kb <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/bounds_f.rds")
bounds_k562_50kb <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/bounds_f.rds")

res <- makeVennDiagram(Peaks=list(bounds_gm12878_50kb, bounds_k562_50kb),
                       NameOfPeaks=c("GM12878", "K562"))

venn_50kb <- venn_cnt2venn(res$vennCounts)
venn_50kb <- compute.Venn(venn_50kb)
gp <- VennThemes(venn_50kb)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "lightblue"
gp[["Face"]][["10"]]$fill <-  "red"
gp[["FaceText"]][["10"]]$cex <- 2
gp[["FaceText"]][["11"]]$cex <- 2
gp[["FaceText"]][["01"]]$cex <- 2
gp[["SetText"]][["Set1"]]$cex <- 2
gp[["SetText"]][["Set2"]]$cex <- 2
#plot(venn_50kb)

@@

#binslist_gm12878_100kb <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/binslist100.rds")
#binslist_gm12878_100kb_center <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/binslist100_center.rds")
#mcols(binslist_gm12878_100kb)$y <- mcols(binslist_gm12878_100kb_center)$y
#binslist_gm12878_100kb <- binslist_gm12878_100kb[mcols(binslist_gm12878_100kb)$y==1]

#binslist_K562_100kb <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/binslist100.rds")
#binslist_K562_100kb_center <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/binslist100_center.rds")
#mcols(binslist_K562_100kb)$y <- mcols(binslist_K562_100kb_center)$y
#binslist_K562_100kb <- binslist_K562_100kb[mcols(binslist_K562_100kb)$y==1]

bounds_gm12878_100kb <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/bounds_f.rds")
bounds_k562_100kb <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/bounds_f.rds")

res <- makeVennDiagram(Peaks=list(bounds_gm12878_100kb, bounds_k562_100kb),
                       NameOfPeaks=c("GM12878", "K562"))

venn_100kb <- venn_cnt2venn(res$vennCounts)
venn_100kb <- compute.Venn(venn_100kb)
gp <- VennThemes(venn_100kb)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "lightblue"
gp[["Face"]][["10"]]$fill <-  "red"
gp[["FaceText"]][["10"]]$cex <- 2
gp[["FaceText"]][["11"]]$cex <- 2
gp[["FaceText"]][["01"]]$cex <- 2
gp[["SetText"]][["Set1"]]$cex <- 2
gp[["SetText"]][["Set2"]]$cex <- 2
#plot(venn_100kb)

@@

gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_5kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("5 kb", gp=gpar(fontsize=50)))
grid.newpage()
gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_10kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("10 kb", gp=gpar(fontsize=50)))
grid.newpage()
gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_25kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("25 kb", gp=gpar(fontsize=50)))
grid.newpage()
gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_50kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("50 kb", gp=gpar(fontsize=50)))
grid.newpage()
gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_100kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("100 kb", gp=gpar(fontsize=50)))
grid.newpage()

### 2019-07-23 Scripts/evaluating_imbalance_ratios.Rmd
updated with preprocessed tads

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)

@@

##Bounds Plots

```{r}
a <- ggplot(bounds_df[which(bounds_df$res=="5kb"),], aes(x=cl, y=TotBounds, fill=cl))+
  geom_bar(stat="identity", position="dodge")+
  theme_minimal() +
  theme_bw()+
  xlab("") + ylab("") + ylim(0,30000) +
  scale_fill_discrete(name="Cell Line") +
  scale_y_continuous(limits = c(0,30000),
                     breaks=c(0,10000,20000,30000),
                     labels=c("0"="0", "10000"="10", "20000"="20", "30000"="30")) +
  ggtitle("5 kb") +
  guides(fill=FALSE) +
  theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

b <- ggplot(bounds_df[which(bounds_df$res=="10kb"),], aes(x=cl, y=TotBounds, fill=cl))+
  geom_bar(stat="identity", position="dodge")+
  theme_minimal() +
  theme_bw()+
  xlab("") + ylab("") + ylim(0,30000) +
  scale_fill_discrete(name="Cell Line") +
  scale_y_continuous(limits = c(0,30000),
                     breaks=c(0,10000,20000,30000),
                     labels=c("0"="0", "10000"="10", "20000"="20", "30000"="30")) +
  ggtitle("10 kb") +
  guides(fill=FALSE) +
  theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

c <- ggplot(bounds_df[which(bounds_df$res=="25kb"),], aes(x=cl, y=TotBounds, fill=cl))+
  geom_bar(stat="identity", position="dodge")+
  theme_minimal() +
  theme_bw()+
  xlab("") + ylab("") + ylim(0,30000) +
  scale_fill_discrete(name="Cell Line") +
  scale_y_continuous(limits = c(0,30000),
                     breaks=c(0,10000,20000,30000),
                     labels=c("0"="0", "10000"="10", "20000"="20", "30000"="30")) +
  ggtitle("25 kb") +
  guides(fill=FALSE) +
  theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

d <- ggplot(bounds_df[which(bounds_df$res=="50kb"),], aes(x=cl, y=TotBounds, fill=cl))+
  geom_bar(stat="identity", position="dodge")+
  theme_minimal() +
  theme_bw()+
  xlab("") + ylab("") + ylim(0,30000) +
  scale_fill_discrete(name="Cell Line") +
  scale_y_continuous(limits = c(0,30000),
                     breaks=c(0,10000,20000,30000),
                     labels=c("0"="0", "10000"="10", "20000"="20", "30000"="30")) +
  ggtitle("50 kb") +
  guides(fill=FALSE) +
  theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

e <- ggplot(bounds_df[which(bounds_df$res=="100kb"),], aes(x=cl, y=TotBounds, fill=cl))+
  geom_bar(stat="identity", position="dodge")+
  theme_minimal() +
  theme_bw()+
  xlab("") + ylab("") + ylim(0,30000) +
  scale_fill_discrete(name="Cell Line") +
  scale_y_continuous(limits = c(0,30000),
                     breaks=c(0,10000,20000,30000),
                     labels=c("0"="0", "10000"="10", "20000"="20", "30000"="30")) +
  ggtitle("100 kb") +
  guides(fill=FALSE) +
  theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

figure <- ggarrange(a,b,c,d,e,
                    ncol=5,
                    nrow=1)
figure
annotate_figure(figure,
    #bottom = text_grob("Cell Line", color = "black", size = 20),
    left = text_grob("Number of TAD Boundary\nRegions (thousands)", color = "black", rot = 90, size=20)
)

>>>>

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(irr)

@@

##Boundary regions Plots

```{r}
a <- ggplot(irtab_summ[which(irtab_summ$res=="5kb"),], aes(x=cl, y=AveBounds, fill=cl))+
  geom_bar(stat="identity", position="dodge")+
  geom_errorbar(aes(ymin=AveBounds-AveBoundsSD, ymax=AveBounds+AveBoundsSD), width=.5,
                 position=position_dodge(.9), alpha=0.75) +
  theme_minimal() +
  theme_bw()+
  xlab("") + ylab("") + ylim(0,2100) +
  scale_fill_discrete(name="Cell Line") +
  scale_y_continuous(limits = c(0,2100),
                     breaks=c(0,500,1000,1500,2000),
                     labels=c("0"="0", "500"="5", "1000"="10", "1500"="15", "2000"="20")) +
  ggtitle("5 kb") +
  guides(fill=FALSE) +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20))

b <- ggplot(irtab_summ[which(irtab_summ$res=="10kb"),], aes(x=cl, y=AveBounds, fill=cl))+
  geom_bar(stat="identity", position="dodge")+
  geom_errorbar(aes(ymin=AveBounds-AveBoundsSD, ymax=AveBounds+AveBoundsSD), width=.5,
                 position=position_dodge(.9), alpha=0.75) +
  theme_minimal() +
  theme_bw()+
  xlab("") + ylab("") + ylim(0,2100) +
  scale_fill_discrete(name="Cell Line") +
  scale_y_continuous(limits = c(0,2100),
                     breaks=c(0,500,1000,1500,2000),
                     labels=c("0"="0", "500"="5", "1000"="10", "1500"="15", "2000"="20")) +
  ggtitle("10 kb") +
  guides(fill=FALSE) +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20))

c <- ggplot(irtab_summ[which(irtab_summ$res=="25kb"),], aes(x=cl, y=AveBounds, fill=cl))+
  geom_bar(stat="identity", position="dodge")+
  geom_errorbar(aes(ymin=AveBounds-AveBoundsSD, ymax=AveBounds+AveBoundsSD), width=.5,
                 position=position_dodge(.9), alpha=0.75) +
  theme_minimal() +
  theme_bw()+
  xlab("") + ylab("") + ylim(0,2100) +
  scale_fill_discrete(name="Cell Line") +
  scale_y_continuous(limits = c(0,2100),
                     breaks=c(0,500,1000,1500,2000),
                     labels=c("0"="0", "500"="5", "1000"="10", "1500"="15", "2000"="20")) +
  ggtitle("25 kb") +
  guides(fill=FALSE) +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20))

d <- ggplot(irtab_summ[which(irtab_summ$res=="50kb"),], aes(x=cl, y=AveBounds, fill=cl))+
  geom_bar(stat="identity", position="dodge")+
  geom_errorbar(aes(ymin=AveBounds-AveBoundsSD, ymax=AveBounds+AveBoundsSD), width=.5,
                 position=position_dodge(.9), alpha=0.75) +
  theme_minimal() +
  theme_bw()+
  xlab("") + ylab("") + ylim(0,2100) +
  scale_fill_discrete(name="Cell Line") +
  scale_y_continuous(limits = c(0,2100),
                     breaks=c(0,500,1000,1500,2000),
                     labels=c("0"="0", "500"="5", "1000"="10", "1500"="15", "2000"="20")) +
  ggtitle("50 kb") +
  guides(fill=FALSE) +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20))

e <- ggplot(irtab_summ[which(irtab_summ$res=="100kb"),], aes(x=cl, y=AveBounds, fill=cl))+
  geom_bar(stat="identity", position="dodge")+
  geom_errorbar(aes(ymin=AveBounds-AveBoundsSD, ymax=AveBounds+AveBoundsSD), width=.5,
                 position=position_dodge(.9), alpha=0.75) +
  theme_minimal() +
  theme_bw()+
  xlab("") + ylab("") + ylim(0,2100) +
  scale_fill_discrete(name="Cell Line") +
  scale_y_continuous(limits = c(0,2100),
                     breaks=c(0,500,1000,1500,2000),
                     labels=c("0"="0", "500"="5", "1000"="10", "1500"="15", "2000"="20")) +
  ggtitle("100 kb") +
  guides(fill=FALSE) +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20))

figure <- ggarrange(a,b,c,d,e,
                    ncol=5,
                    nrow=1)
figure
annotate_figure(figure,
                #bottom = text_grob("Cell Line", color = "black", size = 20),
                left = text_grob("Average number of TBR across chromosomes\n(thousands)", color = "black", rot = 90, size=20)
)
